---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {cranology}: The CRAN Chronology

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/ThinkR-open/cranology/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ThinkR-open/cranology/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `{cranology}` is to provide tools to scrape data from CRAN and MRAN websites as well 
as useful datasets to explore the evolution of the number of packages on CRAN.

## Installation

You can install the development version of `{cranology}` with:

``` r
remotes::install_github("ThinkR-open/cranology")
```

## Examples

```{r example}
library(cranology)
```

### Datasets

All packages ever available on CRAN.

```{r}
cran_packages_history
```

The evolution of the number of packages on CRAN since its beginning.

```{r}
cran_monthly_package_number
```


### Scraping tools

#### CRAN

Both `cran_packages_history` and `cran_monthly_package_number` datasets are generated
by the function `scrape_cran()`. The scraping process is quite time consuming and
relies on the `{furrr}` package to scrape the CRAN pages asynchronously. 

```{r, eval=FALSE}
future::plan(future::multisession)
scrape_cran_history()
```


#### MRAN

`{cranology}` also includes the `get_package_number_mran()` function to more quickly
get the number of packages that were available on CRAN at any given date.

```{r}
dates <- seq(
  from = as.Date("2018-04-10", "%Y-%m-%d"), 
  by = "1 year", 
  length.out = 4
)
get_package_number_mran(dates)
```

Be careful though as this will only work for dates posterior to `2014-09-17` the day when MRAN 
was up online for the first time.

```{r, error=TRUE}
get_package_number_mran("2013-08-28")
```

For earlier dates use `cran_monthly_package_number`. Here is a naïve example:

```{r}
date_before_mran <- as.Date("2013-08-28")

cran_monthly_package_number[
  min(
    which(
      cran_monthly_package_number$date >= date_before_mran
    )
  ), 
]
```

## Acknowledgements

The `scrape_cran()` function is essentially a tidyversification of this [github gist](https://gist.github.com/daroczig/3cf06d6db4be2bbe3368) written by @daroczig.

## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
