---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# {cranology}: The CRAN Chronology

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/ThinkR-open/cranology/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/ThinkR-open/cranology/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of {cranology} is to provide tools to scrape data from CRAN and MRAN websites as well 
as useful datasets to explore the evolution of the number of packages on CRAN.

## Installation

You can install the development version of {cranology} with:

``` r
remotes::install_github("ThinkR-open/cranology")
```

## Examples

```{r example}
library(cranology)
```

### Datasets

```{r}
cran_packages_history
```

```{r}
cran_monthly_package_number
```


### Scraping tools

#### CRAN

```{r}

```


#### MRAN

```{r}
dates <- seq(
  from = as.Date("2018-04-10", "%Y-%m-%d"), 
  by = "1 year", 
  length.out = 4
)
get_package_number_mran(dates)
```


## Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
